Papers

### 2025-01-17 papers.qmd
add published paper

A. Heiskala, **J. D. Tucker**, P. Choudhary, R. Nedelec, J. Ronkainen, O. Sarala, M. Järvelin, M. J. Sillanpääm, and S. Sebert, "Timing based clustering of childhood BMI trajectories reveal differential maturational patterns; Study in the Northern Finland Birth Cohorts 1966 and 1986", *International Journal of Obesity*, accepted, 2024.

>>>>

A. Heiskala, **J. D. Tucker**, P. Choudhary, R. Nedelec, J. Ronkainen, O. Sarala, M. Järvelin, M. J. Sillanpääm, and S. Sebert, "Timing based clustering of childhood BMI trajectories reveal differential maturational patterns; Study in the Northern Finland Birth Cohorts 1966 and 1986", *International Journal of Obesity*, 10.1038/s41366-025-01714-8, 2024. [PDF](Papers/Heiskala_et_al-2025-International_Journal_of_Obesity.pdf)
